---
title: "eds221-day5-activities"
format: html
editor: visual
---

unit test: formal automated check to make sure a piece (unit) of code is behaving unexpectedly

testthat: provides functions that make it easy to describe what you expect a function to do including catching errors, warnings and messages

expect_equal: does the function return an expected value

expect_type: does function return expected type

expect_length: if vector is returned is thee expected length true

expenditure : does function return true

## Test to test for output length

```{r}
fish_mass <- fucntion(alpha, beta, fish_length) {
} 
if (fish_length < 0 ) {
stop("fish length must be greater than zero") 
}
mass <- alpha (fish_length ^beta) 
```

#### If \^ working expectedly

-   if fish length \<0 : should stop function

```{=html}
<!-- -->
```
-   output should be numeric

-   positive value for output

```{r}
expect_length(fish_mass(alpha = 1, beta = 2, fisih_length = 3), 1)
```

-   test length at these values if you use parameters output should be 1

-   create a unit test for expectation the function will return a single value (vecot length of 1)

-   expect length of returned vector for fish mass function evaluated at these values to be 1,

-   if nothing is returned the unit test passes, otherwise an error

ERROR

```{r}
 expect_length(fish_mass(alpha = 1, beta = 2, fisih_length = 3), 2)
```

output inst 1 should be 2, should get an error

## Finding exploring and creating packages 

-   cran r archive network, built packages following very detailed set of restrictions or contents and formatting and styling (https://cran.r-project.org/web/views/)

-   https://ropensci.org support and share software helpful for open data science and creating software and reproducible work

-   PyPI python libraries

-   but google!!

-   open source: source software is software with source code anyone can inspect, modify and enhance

```{r}

```
